Beyond clines: lineages and haplotype blocks in hybrid zones

### 2016-03-07 drafts/supplement.tex
edits

\begin{figure}
    \includegraphics{figs/alleleFrequencies_sim_comparison}
    \caption{
        \textbf{Comparison of simulated to theoretical clines:}
        As in Figure \ref{alleleFreq_tau100},
        frequency of ancestry B,
        across geography and at several physical positions on the genome,
        at $T=100$ generations after secondary contact,
        and at $s=0.1$.
        Dotted lines are expected frequencies of $B$ ancestry $1-q(x,t,r)$
        (unconditional on the ancestry of the linked allele), computed numerically.
        Each line represents a locus some distance $r$ away from the true target of selection, 
        and $r=0$ represents the locus that is under selection.    
    }\label{sfig:alleleFreq_tau100_comparison}
\end{figure}

\begin{figure}
\includegraphics{figs/alleleFrequencies_sim_s01_tau100_closely_linked.pdf}
\caption{
    Frequency of ancestry B,
    across geography and at several physical positions on the genome, simulated for a hybrid zone
     $T=100$ generations after secondary contact,
    and with $s=0.01$.
        50 demes, each with a population size of 500 diploid individuals, were simulated across the hybrid zone.
    Each line represents a locus some distance $r$ away from the true target of selection, 
    and $r=0$ represents the locus that is under selection. Grey lines represent the same positions from a simulation with
    identical parameters except $s=0$.
}\label{alleleFreq_tau100_weaker_s}
\end{figure}

\begin{figure}
\includegraphics{figs/alleleFrequencies_sim_s1_tau1000.pdf}
\caption{
    Frequency of ancestry B,
    across geography and at several physical positions on the genome, simulated for a hybrid zone
     $T=1000$ generations after secondary contact,
    and with $s=0.1$.
        50 demes, each with a population size of 500 diploid individuals, were simulated across the hybrid zone.
    Each line represents a locus some distance $r$ away from the true target of selection, 
    and $r=0$ represents the locus that is under selection. Grey lines represent the same positions from a simulation with
    identical parameters except $s=0$.
 }\label{alleleFreq_tau1000}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{figs/plot_chromosomes_tau100}
\caption{Randomly sampled chromosomes  across a hybrid zone of age $\tau=100$. Here we compare chromosomes of length 1M from a neutral zone to one that has a single under-dominant locus ($s=0.1$) in the middle of the chromosome (indicated by black arrow). Red blocks along the chromosome denote ancestry $B$, and orange blocks are ancestry $A$. Regions surrounding the selected site are failing to introgress.
 }\label{Fig:resistanceToIntrogression100g}
\end{figure}

\begin{figure}
    \includegraphics{{figs/simulation_SIGMA1_Ninds25000_ndemes50_s0.01_tau1000_blocksAlongChromAncBConditioning_nonnormalized}.pdf}
    \caption{
        \textbf{Mean haplotype lengths of $A$ haplotypes}, $l(x,m)$,
        across the genome (horizontal axis) and at differntial spatial locations (colored lines),
        from a simulation with 50 demes having 500 individuals each, $s=0.01$, $\sigma=1$, and after $T=1000$ generations.
    } \label{sfig:blocksAlongChromAncBConditioning_nonnormalized}
\end{figure}

\begin{figure}
\includegraphics{figs/blocksAlongChromHeatmapAncBConditioning}
\caption{Heatmap of mean block length $l_B(m_i)$ along a simulated chromosome. }\label{Supp:blockLengthHeatmap}
\end{figure}

\begin{figure}
\includegraphics{figs/blocksAlongChromNoConditioning}
\caption{Heatmap of mean block length $l_\bullet(m_i)$ surrounding a given position along the genome with a single underdominant site ($s=0.01, \tau=1000$). }\label{Supp:blockLengthNoAnc}
\end{figure}

\begin{figure}
\includegraphics{figs/blocksAlongChromHeatmap}
\caption{Heatmap of mean block length $l_\bullet(m_i)$ along a simulated chromosome with a single underdominant site ($s=0.01, \tau=1000$) }\label{Supp:blockLengthHeatmapNoAnc}
\end{figure}

\begin{figure}
\includegraphics{figs/adjacentBlocksAlongChromAncBConditioning}
\caption{Mean block length of $l_A(m_i\cdot)$ across chromosome with single under dominant site ($s=0.01, \tau=1000$)}\label{Supp:adjacentBlocks}
\end{figure}

\begin{figure}
\includegraphics{figs/ratioAdjacentBlocksAlongChromAncBConditioning}
\caption{Ratio $\frac{2\sum{l_B(m_i)}}{\sum{l_A(m_i-)+I_A(m_i+)}}$ of mean block length and adjacent block lengths across a simulated chromosome with a single underdominant site ($s=0.01, \tau=1000$).  Each line represents a deme and is normalized by mean block length across the chromosome in the deme.}\label{Supp:ratioBlockAdjacent}
\end{figure}

\begin{figure}
\includegraphics{figs/ratioAdjacentBlocksAlongChromHeatmapAncBConditioning}
\caption{Heatmap of $\frac{2\sum{l_B(m_i)}}{\sum{l_A(m_i-)+I_A(m_i+)}}$ across a simulated chromosome with a single underdominant site ($s=0.01, \tau=1000$). }\label{Supp:ratioBlockAdjacentHeatmap}
\end{figure}

\begin{figure}
    \includegraphics{figs/cond_freqs_comparison_tau_80}
    \caption{
        \textbf{Conditional frequencies of ancestry $A$ at $\tau=80$},
        comparing simulation and theory, with $\sigma=3$ deme spacings, $s=0.05$, and 50 individuals per deme.
        The top left figure shows observed and expected genotype frequencies for the two homozygotes and the heterozygote at the selected locus;
        expected genotype counts were obtained assuming random mating,
        and by solving equation \eqref{eqn:cline_pde} numerically.
        The remaining figures show observed and expected frequencies of $A$ ancestry,
        separately conditioned on the identity of the linked allele at the selected site.
        Observed frequencies become much noisier where the linked allele becomes rarer.
    } \label{sfig:condAlleleFreq_tau80_comparison}
\end{figure}

>>>>

\begin{figure}
    \includegraphics{figs/alleleFrequencies_sim_comparison}
    \caption{
        \textbf{Comparison of simulated to theoretical clines:}
        As in Figure \ref{alleleFreq_tau100},
        frequency of ancestry $B$,
        across geography and at several physical positions on the genome,
        at $T=100$ generations after secondary contact,
        and at $s=0.1$.
        Dotted lines are expected frequencies of $B$ ancestry $1-q(x,t,r)$
        (unconditional on the ancestry of the linked allele), computed numerically.
        Each line represents a locus some distance $r$ away from the true target of selection, 
        and $r=0$ represents the locus that is under selection.    
    }\label{sfig:alleleFreq_tau100_comparison}
\end{figure}

\begin{figure}
\includegraphics{figs/alleleFrequencies_sim_s01_tau100_closely_linked.pdf}
\caption{
    Frequency of ancestry $B$,
    across geography and at several physical positions on the genome, simulated for a hybrid zone
     $T=100$ generations after secondary contact,
    and with $s=0.01$.
        50 demes, each with a population size of 500 diploid individuals.
    Each line represents a locus some distance $r$ away from the true target of selection, 
    and $r=0$ represents the locus that is under selection. Grey lines represent the same positions from a simulation with
    identical parameters except that $s=0$.
}\label{alleleFreq_tau100_weaker_s}
\end{figure}

\begin{figure}
\includegraphics{figs/alleleFrequencies_sim_s1_tau1000.pdf}
\caption{
    Frequency of ancestry $B$,
    across geography and at several physical positions on the genome, simulated for a hybrid zone
     $T=1000$ generations after secondary contact,
    and with $s=0.1$.
        50 demes, each with a population size of 500 diploid individuals.
    Each line represents a locus some distance $r$ away from the true target of selection, 
    and $r=0$ represents the locus that is under selection. Grey lines represent the same positions from a simulation with
    identical parameters except that $s=0$.
 }\label{alleleFreq_tau1000}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{figs/plot_chromosomes_tau100}
\caption{Randomly sampled chromosomes  across a hybrid zone of age $T=100$. Here we compare chromosomes of length 1M from a neutral zone to one that has a single under-dominant locus ($s=0.1$) in the middle of the chromosome (indicated by black arrow). Red blocks along the chromosome denote ancestry $B$, and orange blocks are ancestry $A$.
 }\label{Fig:resistanceToIntrogression100g}
\end{figure}

\begin{figure}
    \includegraphics{{figs/simulation_SIGMA1_Ninds25000_ndemes50_s0.01_tau1000_blocksAlongChromAncBConditioning_nonnormalized}.pdf}
    \caption{
        \textbf{Mean haplotype lengths of $A$ haplotypes} \alisa{Should this be $B$ haplotypes? That is what the figure title seems to indicate}, $l(x,m)$ \alisa{this would need to be changed to either $l_A$ or $l_B$},
        across the genome (horizontal axis) and at differntial spatial locations (colored lines),
        from a simulation with 50 demes having 500 individuals each, $s=0.01$, $\sigma=1$, and after $T=1000$ generations.
    } \label{sfig:blocksAlongChromAncBConditioning_nonnormalized}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{{figs/results_runid_753324_chr1_start0.48_stop0.52_by0.001_blocksAlongChromNoConditioning_nonnormalized}.pdf}
\caption{
    \textbf{Mean enclosing block length $l(m,x)$}, across the genome (horizontal axis)
    and at different geographic positions (different colored lines).
    Results are from a simulation with 120 demes of 200 diploids each, selection $s=.05$, dispersal $\sigma=3$, 
    and after $T=500$ generations.
}\label{Fig:meanBlockLengthsUnconditioned}
\end{figure}

\begin{figure}
\includegraphics{figs/blocksAlongChromAncBConditioning}
\caption{
    \textbf{Normalized mean enclosing block length}, $l_B(m,x)$, after $T=1000$ generations,
    against position relative to the selected locus (horizontal axis)
    located in the center of a 1M chromosome.
    Each line shows the mean block length at that spatial and genomic position
    divided by the mean over the chromosome at that location;
    the simulation was run with $s=1$ and $\sigma=1$,
    50 demes, each containing 500 diploid individuals.
}\label{Fig:blockLengths}
\end{figure}

\begin{figure}
\includegraphics{figs/blocksAlongChromHeatmapAncBConditioning}
\caption{Heatmap of mean block length $l_B(m)$ along a simulated chromosome. }\label{Supp:blockLengthHeatmap}
\end{figure}

\begin{figure}
\includegraphics{figs/blocksAlongChromNoConditioning}
\caption{Heatmap of mean block length $l(m)$ surrounding a given position along the genome with a single underdominant site ($s=0.01, T=1000$). }\label{Supp:blockLengthNoAnc}
\end{figure}

\begin{figure}
\includegraphics{figs/blocksAlongChromHeatmap}
\caption{Heatmap of mean block length $l(m)$ along a simulated chromosome with a single underdominant site ($s=0.01, T=1000$) }\label{Supp:blockLengthHeatmapNoAnc}
\end{figure}

\begin{figure}
\includegraphics{figs/adjacentBlocksAlongChromAncBConditioning}
\caption{Mean block length of $l_A(m\pm)$ across chromosome with single under dominant site, conditioning on ancestry $B$ at the selected locus. ($s=0.01, T=1000$)}\label{Supp:adjacentBlocks}
\end{figure}

\begin{figure}
\includegraphics{figs/ratioAdjacentBlocksAlongChromAncBConditioning}
\caption{Ratio $\frac{2\sum{l_B(m_i)}}{\sum{l_A(m_i-)+I_A(m_i+)}}$ of mean block length and adjacent block lengths across a simulated chromosome with a single underdominant site and conditioning on ancestry $B$ at the selected site ($s=0.01, T=1000$).  Each line represents a deme and is normalized by mean block length across the chromosome in the deme.}\label{Supp:ratioBlockAdjacent}
\end{figure}

\begin{figure}
\includegraphics{figs/ratioAdjacentBlocksAlongChromHeatmapAncBConditioning}
\caption{Heatmap of $\frac{2\sum{l_B(m_i)}}{\sum{l_A(m_i-)+I_A(m_i+)}}$ across a simulated chromosome with a single underdominant site and conditioning on ancestry $B$ at the selected site ($s=0.01, T=1000$). }\label{Supp:ratioBlockAdjacentHeatmap}
\end{figure}

\begin{figure}
    \includegraphics[height=0.8\textheight]{figs/cond_freqs_comparison_tau_80}
    \caption{
        \textbf{Conditional frequencies of ancestry $A$ at $\tau=80$},
        comparing simulation and theory, with $\sigma=3$ deme spacings, $s=0.05$, and 50 individuals per deme.
        The top left figure shows observed and expected genotype frequencies for the two homozygotes and the heterozygote at the selected locus;
        expected genotype counts were obtained assuming random mating,
        and by solving equation \eqref{eqn:cline_pde} numerically.
        The remaining figures show observed and expected frequencies of $A$ ancestry,
        separately conditioned on the identity of the linked allele at the selected site.
        Observed frequencies become much noisier where the linked allele becomes rarer.
    } \label{sfig:condAlleleFreq_tau80_comparison}
\end{figure}
